Numerous variables relating to 2016 election in 2021 US GSS^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-03-19 outputs/paper/paper.Rmd
edit some

# Introduction
1) broader context to motivate
2) some detail about hat the papaer is about
3) a clear gap that needs to be filled
4) what was done
5) what was found
6) why it is important
7) The structure of the paper
(3~4 paragraphs)
Donald Trump won the 2016 United States presidential election. We are not US citizens. 
However, considering

@@

Now, let's get into the variables in details. One thing that we focused at first was whether respondents were equivalently recruited. To do this, we have to look at respondents' personal information. If you take a look from figure \@ref(fig:fig1) to \@ref(fig:fig4). We can see some interesting observations as followed:
1) number of survey participants of age in the range of 20~40 is unexpectedly low compared to other ages.
2) There are more white race than others. However, considering US race demographics, it is very reasonable. 
For more details on US race demographics, please visit the link below: https://www.census.gov/quickfacts/fact/table/US/PST045221.
3) For gender, there is slightly more female than male, and we will see later whether this has impacts on vote or not. 
4) Clinton's vote is higher than trump's vote in this survey, which contradicts the election result of 2016, reader should keep in mind that this survey is more biased towards Clinton.

From figure \@ref(fig:fig5) to \@ref(fig:fig14), they represent respondents' thoughts on national policies as well as relation between variables.  
Mostly they were collected from questions that whether you think that national spending on corresponding variables is about right, too much, or too little.
For instance, let's take a look at figure \@ref(fig:fig7). This graph represents respondents' thoughts on U.S national spending on improving black condition, and we sorted it with our interest, Clinton or Trump. For more example, let's take a look at figure \@ref(fig:fig9).This graph represents relation between income and degree with respect to our interest. It generally shows that higher education you have more income you earn. We are going to talk about interesting results in more detailed later in result and discussion session. For more information regarding variables graph please check Appendix.

@@

# Appendix {-}
Figure \@ref(fig:fig6) represents people who were born in US and their votes on the candidates. Most respondents were born in US.
Figure \@ref(fig:fig8) represents national spending on welfare. People who advocated more funds in improvement of welfare shows preference in Clinton and people who did not shows preference in Trump. 
Figure \@ref(fig:fig10) represents whether U.S should limit immigration in order to protect their own cultures or not. Even though many answered "Not Applicable", we can observe two different patters in Clinton and Trump. 
Figure \@ref(fig:fig11) represents  national spending on education with votes. People who want more funds in education improvement shows preference in Clinton and vice versa.
Figure \@ref(fig:fig12) represents national spending on the arms with respect to votes for the candidates. People who thought too much clealry shows the preference toward Clinton. 
Figure \@ref(fig:fig13) represents national spending on the poor with respect to respondents' votes on the candidates. From "About right" to "Too much", there exits more Trump supporters than Clinton's and vice versa.
Figure \@ref(fig:fig14) represents national spending on aids to foreign countries with respect to the votes for candidates . There exists more Trump supporters in "Too much" comparing to Clinton's supporters.

>>>>

# Introduction
Donald Trump won the 2016 United States presidential election. From what we remembered, it was quite surprising considering his image outside of U.S or even in U.S. Also, from what we remembered, before the election, Hillary Clinton was winning in most surveys as well. There is a famous quote that we learn from the past. Therefore, we thought that even though we are living in 2022, it would be meaningful to analyze the election so that we get to know what U.S citizens thoughts, or in broad sense thoughts trends in nowadays and what factors they or we considered most important to decide our representative.

This paper is going to explore mainly possible variables that potentially had impacts on deciding factors in the election as well as their analysis. However, making a decision that this variable affects U.S citizens to lean on Trump side or Clinton side is not easy because there is nothing in this world absolute. Thus, as we mentioned above, we are going to focus on general flows of results instead of defining variables as absolute factors of the demarcation. Following that, this paper has structures: Data, Results, Discussion, Appendix and supplementary survey.

We have obtained dataset from U.S GSS, and sorted variables that we consider as potential factors affecting the election. Throughout analysis of relation between the variables and respondents' votes on the election, we could observe that people who have conservative thoughts on equality and welfare preferred Trump, and people who do not preferred Clinton. This may sound obvious considering their parties, however in result session, reader can observe that what specific areas or fields they become more conservative and progressive. We believe that this situation is not only happening in U.S, but it also happens all over the world. This claim is going to be conducted with supplementary survey session.

@@

Now, let's get into the variables in details. One thing that we focused at first was whether respondents were equivalently recruited. To do this, we have to look at respondents' personal information. If you take a look from figure \@ref(fig:fig1) to \@ref(fig:fig4). We can see some interesting observations as followed:

1) number of survey participants of age in the range of 20~40 is unexpectedly low compared to other ages.

2) There are more white race than others. However, considering US race demographics, it is very reasonable. 
For more details on US race demographics, please visit the link: https://www.census.gov/quickfacts/fact/table/US/PST045221.

3) For gender, there is slightly more female than male, and we will see later whether this has impacts on vote or not.

4) Clinton's vote is higher than trump's vote in this survey, which contradicts the election result of 2016, reader should keep in mind that this survey is more biased towards Clinton.

From figure \@ref(fig:fig5) to \@ref(fig:fig14), they represent respondents' thoughts on national policies as well as relation between variables. Mostly they were collected from questions that whether you think that national spending on corresponding variables is about right, too much, or too little.For instance, let's take a look at figure \@ref(fig:fig7). This graph represents respondents' thoughts on U.S national spending on improving black condition, and we sorted it with our interest, Clinton or Trump. For more example, let's take a look at figure \@ref(fig:fig9).This graph represents relation between income and degree with respect to our interest. It generally shows that higher education you have more income you earn. We are going to talk about interesting results in more detailed later in result and discussion session. For more information regarding variables graph please check Appendix.

@@

# Appendix {-}
1) Figure \@ref(fig:fig6) represents people who were born in US and their votes on the candidates. Most respondents were born in US.

2) Figure \@ref(fig:fig8) represents national spending on welfare. People who advocated more funds in improvement of welfare shows preference in Clinton and people who did not shows preference in Trump.

3) Figure \@ref(fig:fig10) represents whether U.S should limit immigration in order to protect their own cultures or not. Even though many answered "Not Applicable", we can observe two different patters in Clinton and Trump.

4) Figure \@ref(fig:fig11) represents  national spending on education with votes. People who want more funds in education improvement shows preference in Clinton and vice versa.

5) Figure \@ref(fig:fig12) represents national spending on the arms with respect to votes for the candidates. People who thought too much clealry shows the preference toward Clinton.

6) Figure \@ref(fig:fig13) represents national spending on the poor with respect to respondents' votes on the candidates. From "About right" to "Too much", there exits more Trump supporters than Clinton's and vice versa.

7) Figure \@ref(fig:fig14) represents national spending on aids to foreign countries with respect to the votes for candidates . There exists more Trump supporters in "Too much" comparing to Clinton's supporters.
